### 2014-01-23 Draft/evaluation.tex
publishing local file changes

We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address three main research questions:

\begin{itemize}

\item\textbf{RQ1}: What are the precision and recall of \tool\ in inferring usage constraints?

%\item\textbf{RQ2}: What is the accuracy of our approach in inferring specifications from contract sentences in the API documents?

\item\textbf{RQ2}: How does our approach fares in comparison to previous NLP approaches?

\end{itemize}

@@

We used the API documents of the following two libraries as subjects for our evaluation.

\amazon\ provides a simple REST based web services interface that can be used to store and retrieve data on the web. Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure. \textbf{may be a little detail of usage statistics etc....}

\textbf{TBD}.

@@

>>>>

We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address two main research questions:

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
	identifying temporal contraints from sentences written in natural language?
	%\item\textbf{RQ2}: What is the accuracy of our approach in inferring specifications from contract sentences in the API documents? 
	\item\textbf{RQ2}: How does our approach fares in comparison to previous NLP approaches?
\end{itemize}

@@

We used the API documents of the following two libraries as subjects for our evaluation. 
\begin{itemize}
	\item{Amazon S3}. \amazon\ provides a REST based web services interface that can be used to store and retrieve data on the web. Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure. \CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.

	\item{java.io}. \CodeIn{java.io} is a popular packacge in \CodeIn{Java} programming language that provides APIs for system input and output through data streams, serialization and the file system.
\end{itemize}
We chose \CodeIn{Amazon S3} and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.

\subsection{Experimental Setup.} 
We apply our approach on the API documents of the two APIs.
To determine the precision and recall, 
two authors manually label each sentence in the API documentation as sentence containing 
temporal constraints or not. After the authors have classified all the sentences, they 
talk to each ther to reach a consensus on the sentences they classified differently. 
We use this classified scentes as the golden set for calculating precision and recall.

\CodeIn{cohen kappa} score of the two authors was 6.6

@@

If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.

If markposMM is -1MM (no mark has been set or the mark has been invalidated), an IOExceptionMM is thrown.
